Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-05-14 AppendixI.Rmd
Appendix, PCA graphs

@@

@@

# Figure A2

@@

# Figure A3

```{r DivFunAppendix, out.width = '60%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure*"}
load("DB/FunctionalTraj_ForGraphsnew")

@@

>>>>

(ref:Bolda) **(a)**

(ref:Boldb) **(b)**

(ref:Boldc) **(c)**

@@

**Figure A4**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:PCA_graphs).

**Figure A5**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:RedFun).

@@

# **Figure A2**: Proportion of seed mass classes along time

@@

# **Figure A3**: Rao diversity trajectories with all plots display

```{r DivFunAppendix, out.width = '60%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure*"}
load("DB/FunctionalTraj_ForGraphs")

@@

# **Figure A4**: Functional PCA

```{r PCA_graphs, out.width = '100%', echo=FALSE, fig.cap="Summarizing plots of the functional PCA analysis defining communities functional space. (ref:Bolda) Plot of the samples from the BRIDGE functional database in the two dimensional main plan. (ref:Boldb) bow plot of the PCA eignevalues in percentage. (ref:Boldc) Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem traits, and maximum species height).", fig.env="figure*"}
load("DB/FunctionalPCA")

plotPCA(DataACP)

# **Figure A5**: Overall functional redundancy

```{r RedFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/Redundancy")

par(mar=c(5,4,5,2))
RedundancyPlot(RedundancyTraj)
mtext("Functional Redundancy",side=3,adj=0,line=1.5)
mtext("Restricted to initial functional space",side=3,adj=0,cex=0.8,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1)

### 2018-05-14 AppendixI.tex
appendix & graphs
Appendix, PCA graphs

\JournalInfo{Hal 00679993} % Journal information
\Archive{} % Additional notes (e.g. copyright, DOI, review/research article)

@@

@@

\section{Figure A2}\label{figure-a2}

@@

\section{Figure A3}\label{figure-a3}

@@

@@

\bibliographystyle{mee}
\bibliography{}

>>>>

\JournalInfo{Hal 00679993} % Journal information
\Archive{\ }

@@

\textbf{Figure A4}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. @ref(fig:PCA\_graphs).

\textbf{Figure A5}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. \ref{fig:RedFun}.

@@

\section{\texorpdfstring{\textbf{Figure A2}: Proportion of seed mass
classes along
time}{Figure A2: Proportion of seed mass classes along time}}\label{figure-a2-proportion-of-seed-mass-classes-along-time}

@@

\section{\texorpdfstring{\textbf{Figure A3}: Rao diversity trajectories
with all plots
display}{Figure A3: Rao diversity trajectories with all plots display}}\label{figure-a3-rao-diversity-trajectories-with-all-plots-display}

@@

\section{\texorpdfstring{\textbf{Figure A4}: Functional
PCA}{Figure A4: Functional PCA}}\label{figure-a4-functional-pca}

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/PCA_graphs-1}

\caption{Summarizing plots of the functional PCA analysis defining communities functional space. \textbf{(a)} Plot of the samples from the BRIDGE functional database in the two dimensional main plan. \textbf{(b)} bow plot of the PCA eignevalues in percentage. \textbf{(c)} Plot of the 7 functional traits sed in the PCA analysis (Leaf and stem traits, and maximum species height).}(\#fig:PCA_graphs)
\end{figure*}

\section{\texorpdfstring{\textbf{Figure A5}: Overall functional
redundancy}{Figure A5: Overall functional redundancy}}\label{figure-a5-overall-functional-redundancy}

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/RedFun-1}

\caption{Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:RedFun}
\end{figure*}

@@

\bibliographystyle{mee}
\makeatletter
% The filename has .bib extension the must be eliminated
\filename@parse{}
% parse stores the file name in base. Extension starts at the first dot, so don't use dots in file names.
\bibliography{\filename@base}
\makeatother

### 2018-05-14 WholePlotTrajectories.Rmd
Appendix, PCA graphs

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

@@

```{r NMDSplans, out.width = '100%', fig.asp = 1.2/2, echo=FALSE, fig.cap="Trajectories of the plots in terms of (ref:Bolda) flora composition and (ref:Boldb) functional composition regarding the 6 leaf and stem functional traits,the maximum allometric height and seed mass class in the two-dimensional space from the NMDS performed for the 30 years after disturbance. Distance matrix for NMDS were computed from the Bray-curtis dissimilarity between successive inventories. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3).", fig.env="figure"}
load("DB/FunctionalComposition_forGraph")
load("DB/TaxoComposition_forGraphs")

TaxoCompo(MatrepTaxo)
FunCompo(MatrepFun)

@@

plotIDH(Data=Sim,AgbLoss=AGBloss)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("initial %AGB lost",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.28,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

The functional redundancy was measured as the sum of weighted overlap among species in the communities.
Species functional space were defined in the main two-dimensional space of a PCA analysis based on all leaf and stem and maximum height traits (see appendix I for more details). 
Plots functional redundancy compared to the initial value after logging so that only communities dynamics are followed apart from the impact of logging itself.
Communities functional redundancy remained stable in control plots but after disturbance the redundancy trajectories were quite variable (See appendix I).
Globally after most intense disturbance (plots T2 and T3) communities redundancy decreased at first place and then increased to edge, recover or even exceed the initial value.
Considering the functional redundancy restricted to the functional space of the initial inventory, though, all disturbed plots followed similar decreasing humped-shaped trajectories (\@ref(fig:RedFun)).
The maximum redundancy loss observed was positively correlated with the disturbance intensity (XX spearman to be measured) and none of the disturbed plots had recovered the functional redundancy within their initial functional space.

```{r RedFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes.Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure"}
load("DB/Redundancy_restricted")

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

```{r NMDSplans, out.width = '100%', fig.asp = 1.2/2, echo=FALSE, fig.cap="Trajectories of the plots in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) regarding the 6 leaf and stem functional traits, the maximum allometric height and seed mass class. Plots trajectories are first represented in the two-dimensional space from the NMDS performed for the 30 years after disturbance based on Bray-Curtis dissimilarity measures between successive inventories (Upper panels (ref:Bolda) and (ref:Boldb)). Then the lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.", fig.env="figure*"}
load("DB/FunctionalComposition_forGraph");load("DB/TaxoComposition_forGraphs")
load("DB/FunctionalComposition_forGraph");load("DB/TaxoComposition_forGraphs")

par(mfrow=c(2,2))
TaxoCompo(MatrepTaxo)
FunCompo(MatrepFun)
TaxoDist(MatrepTaxo)
FunDist(MatrepFun)

@@

plotIDH(Data=Sim,AgbLoss=AGBloss)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("initial %AGB lost",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.28,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")
```

The functional redundancy was measured as the sum of weighted overlap among species in communities' functional space.
Functional space were defined in the main two-dimensional space of a PCA analysis based on all leaf and stem and maximum height traits (see appendix I for PCA details). 
Plots functional redundancy compared to the initial value after logging so that only communities dynamics are followed apart from the impact of logging itself.
Communities functional redundancy remained stable in control plots but after disturbance the redundancy trajectories were quite variable (See appendix I).
Globally after most intense disturbance (plots T2 and T3) communities redundancy decreased at first place and then increased to edge, recover or even exceed the initial value.
Considering the functional redundancy restricted to the functional space of the initial inventory, though, all disturbed plots followed similar decreasing humped-shaped trajectories (\@ref(fig:RedFun_rest)).
The maximum redundancy loss observed was positively correlated with the disturbance intensity (XX spearman to be measured) and none of the disturbed plots had recovered the functional redundancy within their initial functional space.

```{r RedFun_rest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial cpùùunities functional space over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure"}
load("DB/Redundancy_restricted")

### 2018-05-14 WholePlotTrajectories.tex
Appendix, PCA graphs

In tropical forest, ecological communities are contantly re-shaped by
the natural disturbance events that changes the abiotic environment,
through the fluxes of light, heat and water, and the biotic interaction
and competitive pressure \emph{(Goulamoussene Biogeosciences)}. The
cornerstone of tropical forests ecology is then to understand the
underlyings of ecosystem response to disturbance, its mechanisms and
drivers \citep{White2001, Chazdon2003a}. For now, this has been largely
studied through structural parameters, rapid and convenient to measure,
as aboveground biomass, tree height or stem density
\emph{(e.g.~PiponiotElife, RutishauserBiotropica)}. These structural
parameters have then been sucessfully modeled and allowed to assess the
maintenance of ecosystems processes and services
\citep{Denslow2000, Blanc2009, Rutishauser2016}. However the response of
tree species diversity remains unclear, also it is determinant of
ecosystems productivity, stability and functioning
\citep[Liang2016Science]{Tilman2014} and would be most probably impacted
by post-disturbance environmental changes \citep{BaralotoJAE}.

In the short-term disturbance demonstrated negligible or even positive
impacts on communities diversity, which have been formalized by the
intermediate disturbance hypothesis (IDH) stating a maximized species
diversity at intermediate disturbance intensity
\citep{Molino2001, Kariuki2006a, Berry2008a}. Validations of the IDH in
the long term, however, remain scarce and mainly rely on the analysis of
the rough species richness that gives limited or misleading information
on forests recovery and functioning \citep{Martin2015, Chaudhary2016}.
More releveant monitoring would encompass communities composition, that
is crucial for conservation issues, and diversity profiles, that reveals
ecological rules underlying communities' structure
\citep{Magurran1988, Lavorel2002, Bellwood2006}. Furthermore, the
functional approach accounting for differenes species biological
attributes would be insightful as it reveals the species role in the
post-disturbance trajectory of ecosystems functioning
\citep{Violle2007b, Moretti2009, Baraloto2012a, Scheiter2013}. In that
respect major functional traits related to species ecology and
performance were largely adopted through an integrative framework
\citep{Diaz2005, Villeger2008a}. The functional trait-based approach,
for example, highlighted in tropical rainforests the environmental
filters fostering disturbance resistant species with rapid growth and
efficient resources acquisition \citep{Molino2001, Haddad2008}. In
disturbed tropical rainforests, this framework translates into the
fostering disturbance resistant species with rapid growth and efficient
resources acquisition \citep{Molino2001, Haddad2008} with a shift from
``conservative'' slow-growing species dealing with scarce resources that
dominate before disturbance, to ``acquisitive'' fast-growing species
with rapid and efficient use of abundant resources
\citep{TerSteege2001, Reich2014, Herault2011}. It was mirrored by shifts
in key functional traits related to resource acquisition (leaf area,
density and chlorophyll content, and stem specific gravity and bark
thickness), tree growth and reproduction life history traits (seed mass
and maximum height) \citep{Wright2004, Westoby2006a, Chave2009b}.

@@

\caption{Trajectories of the plots in terms of \textbf{(a)} flora composition and \textbf{(b)} functional composition regarding the 6 leaf and stem functional traits,the maximum allometric height and seed mass class in the two-dimensional space from the NMDS performed for the 30 years after disturbance. Distance matrix for NMDS were computed from the Bray-curtis dissimilarity between successive inventories. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3).}\label{fig:NMDSplans}
\end{figure}

@@

The functional diversity trajectories of plots based on the 8 leaf, stem
and life history traits was examined through the Rao diversity. For all
undisturbed plots the functional diversity remained comparable to the
reference values 5 years after disturbance (1989 inventories). For all
disturbed plots the functional trajectories followed a unimodal
trajectory with a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}=0.73\)) (Figure \ref{fig:DivFun}). The plot 7 from
treatment 1 that displayed a constantly outlying diversity was removed
from the graphical representation for better readability, see appendix
for full graph. Thirty years after disturbance all plots, whenever the
initial disturbance intensity, regained diversity values similar to
their initial value and to those of control plots.

@@

The functional redundancy was measured as the sum of weighted overlap
among species in the communities. Species functional space were defined
in the main two-dimensional space of a PCA analysis based on all leaf
and stem and maximum height traits (see appendix I for more details).
Plots functional redundancy compared to the initial value after logging
so that only communities dynamics are followed apart from the impact of
logging itself. Communities functional redundancy remained stable in
control plots but after disturbance the redundancy trajectories were
quite variable (See appendix I). Globally after most intense disturbance
(plots T2 and T3) communities redundancy decreased at first place and
then increased to edge, recover or even exceed the initial value.
Considering the functional redundancy restricted to the functional space
of the initial inventory, though, all disturbed plots followed similar
decreasing humped-shaped trajectories (\ref{fig:RedFun}). The maximum
redundancy loss observed was positively correlated with the disturbance
intensity (XX spearman to be measured) and none of the disturbed plots
had recovered the functional redundancy within their initial functional
space.

@@

{\centering \includegraphics[width=1\linewidth]{WholePlotTrajectories_files/figure-latex/RedFun-1}

@@

\caption{Trajectories of the functional redundancy over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes.Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:RedFun}
\end{figure}

>>>>

In tropical forest, ecological communities are contantly re-shaped by
the natural disturbance events that changes the abiotic environment,
through the fluxes of light, heat and water, and the biotic interaction
and competitive pressure \citep{Goulamoussene2017}. The cornerstone of
tropical forests ecology is then to understand the underlyings of
ecosystem response to disturbance, its mechanisms and drivers
\citep{White2001, Chazdon2003a}. For now, this has been largely studied
through structural parameters, rapid and convenient to measure, as
aboveground biomass, tree height or stem density
\citep{Piponiot2016, Rutishauser2016}. These structural parameters have
then been sucessfully modeled and allowed to assess the maintenance of
ecosystems processes and services \citep{Denslow2000, Blanc2009}.
However the response of tree species diversity remains unclear, also it
is determinant of ecosystems productivity, stability and functioning
\citep[\citet{Liang2016}]{Tilman2014} and would be most probably
impacted by post-disturbance environmental changes
\citep{Baraloto2012a}.

In the short-term disturbance demonstrated negligible or even positive
impacts on communities diversity, which have been formalized by the
intermediate disturbance hypothesis (IDH) stating a maximized species
diversity at intermediate disturbance intensity
\citep{Molino2001, Kariuki2006a, Berry2008a}. Validations of the IDH in
the long term, however, remain scarce and mainly rely on the analysis of
the rough species richness that gives limited or misleading information
on forests recovery and functioning \citep{Martin2015, Chaudhary2016}.
More releveant monitoring would encompass communities composition, that
is crucial for conservation issues, and diversity profiles, that reveals
ecological rules underlying communities' structure
\citep{Magurran1988, Lavorel2002, Bellwood2006}. Furthermore, the
functional approach accounting for differenes species biological
attributes would be insightful as it reveals the species role in the
post-disturbance trajectory of ecosystems functioning
\citep{Violle2007b, Moretti2009, Baraloto2012a, Scheiter2013}. In that
respect major functional traits related to species ecology and
performance were largely adopted through an integrative framework
\citep{Diaz2005, Villeger2008a}. The functional trait-based approach,
for example, highlighted in tropical rainforests the environmental
filters fostering disturbance resistant species with rapid growth and
efficient resources acquisition \citep{Molino2001, Haddad2008}. In
disturbed tropical rainforests, this framework translates into the
fostering of disturbance resistant species with rapid growth and
efficient resources acquisition \citep{Molino2001, Haddad2008}. It
results in a shift from ``conservative'' slow-growing species dealing
with scarce resources that dominate before disturbance, to
``acquisitive'' fast-growing species with rapid and efficient use of
abundant resources \citep{TerSteege2001, Reich2014, Herault2011}. It was
mirrored by shifts in key functional traits related to resource
acquisition (leaf area, density and chlorophyll content, and stem
specific gravity and bark thickness), tree growth and reproduction life
history traits (seed mass and maximum height)
\citep{Wright2004, Westoby2006a, Chave2009b}.

@@

\caption{Trajectories of the plots in terms of flora composition (left panels \textbf{(a)} and \textbf{(c)}) and functional composition (right panels \textbf{(b)} and \textbf{(d)}) regarding the 6 leaf and stem functional traits, the maximum allometric height and seed mass class. Plots trajectories are first represented in the two-dimensional space from the NMDS performed for the 30 years after disturbance based on Bray-Curtis dissimilarity measures between successive inventories (Upper panels \textbf{(a)} and \textbf{(b)}). Then the lower panels (\textbf{(c)} and \textbf{(d)}) represent the euclidean distance to initial condition along the 30 sampled years. Line colors represent the disturbance treatment (green for control, blue for T1,orange for T2 and red for T3). The 0.025 and 0.975 percentile correspond to the variance observed for 50 iteration of the taxonomic uncertainty propagation and functional trait filling processes.}\label{fig:NMDSplans}
\end{figure*}

@@

The functional diversity trajectories of plots based on the 8 leaf, stem
and life history traits was examined through the Rao diversity. For all
undisturbed plots the functional diversity remained comparable to the
reference values 5 years after disturbance (1989 inventories). For all
disturbed plots the functional trajectories followed a unimodal
trajectory with a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}=0.73\)) (Figure \ref{fig:IDHplot}). The plot 7 from
treatment 1 that displayed a constantly outlying diversity was removed
from the graphical representation for better readability, see appendix
for full graph. Thirty years after disturbance all plots, whenever the
initial disturbance intensity, regained diversity values similar to
their initial value and to those of control plots.

@@

The functional redundancy was measured as the sum of weighted overlap
among species in communities' functional space. Functional space were
defined in the main two-dimensional space of a PCA analysis based on all
leaf and stem and maximum height traits (see appendix I for PCA
details). Plots functional redundancy compared to the initial value
after logging so that only communities dynamics are followed apart from
the impact of logging itself. Communities functional redundancy remained
stable in control plots but after disturbance the redundancy
trajectories were quite variable (See appendix I). Globally after most
intense disturbance (plots T2 and T3) communities redundancy decreased
at first place and then increased to edge, recover or even exceed the
initial value. Considering the functional redundancy restricted to the
functional space of the initial inventory, though, all disturbed plots
followed similar decreasing humped-shaped trajectories
(@ref(fig:RedFun\_rest)). The maximum redundancy loss observed was
positively correlated with the disturbance intensity (XX spearman to be
measured) and none of the disturbed plots had recovered the functional
redundancy within their initial functional space.

@@

{\centering \includegraphics[width=1\linewidth]{WholePlotTrajectories_files/figure-latex/RedFun_rest-1}

@@

\caption{Trajectories of the functional redundancy within the initial cpùùunities functional space over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}(\#fig:RedFun_rest)
\end{figure}
